---
title: "Data documentation"
author: "Claudius Gräbner"
date: "29 3 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Documentation of the data

## Information about variables

Here are the information about the variables in the data set. You can also look at `src/data_preparation.R` to see how the data set gets created.

| Variable                    | Description                                                                         | Unit               | Source           |
| ----------------------------|-------------------------------------------------------------------------------------|:------------------:|:----------------:|
| location_code               | The iso3 country code                                                               | iso3c              | [Info][1]        |
| year                        | The year of observation                                                             |                    |                  |
| trade_to_gdp                | Sum of exports and imports of goods and services measured as a share of GDP.        | % of GDP           | [World Bank][2]  |
| exp_to_gdp                  | Value of all goods and other market services provided to the rest of the world      | % of GDP           | [World Bank][3]  |
| imp_to_gdp                  | Value of all goods and other market services received from the rest of the world.   | % of GDP           | [World Bank][4]  |
| exp_minus_imp               | `exp_to_gdp` minus `imp_to_gdp`                                                     | % of GDP           | Own calculation  |
| res_rents                   | Total natural ressource rents                                       | % of GDP     | [World Bank][5]  |
| oil_exports_share           | Share of oil in good exports (28, 32, 35, 68, 97, 5224, 5231, 5232, 5233)           | % of total exports | [MIT][6] or [HARV][7] Atlas, own calculation  |
| coal_metal_export_share     | Share of coals and metals in good exports (SITC codes 33 and 34)                    | % of total exports | [MIT][6] or [HARV][7] Atlas, own calculation  |
| primary_exports_share_1     | Share of primary goods (SITC codes 0, 1, 2, 4)                                      | % of total exports | [MIT][6] or [HARV][7] Atlas, own calculation  |
| primary_exports_share_2     | Alternative share of primary goods (SITC codes 0, 1, 2, 4 and 3)                    | % of total exports | [MIT][6] or [HARV][7] Atlas, own calculation  |

[1]: https://unstats.un.org/unsd/tradekb/knowledgebase/country-code
[2]: https://data.worldbank.org/indicator/NE.TRD.GNFS.ZS
[3]: https://data.worldbank.org/indicator/ne.exp.gnfs.zs
[4]: https://data.worldbank.org/indicator/NE.IMP.GNFS.ZS
[5]: https://data.worldbank.org/indicator/ny.gdp.totl.rt.zs
[6]: https://atlas.media.mit.edu/en/
[7]: http://atlas.cid.harvard.edu/downloads 


## Descriptive statistics

Here is more information about the data that uses the MIT export data:
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
mit_descriptives <- read_csv("../data/dimension_endownment_data_MIT.csv") %>%
  tidyr::gather(variable, value, -location_code, -year) %>%
  group_by(variable) %>%
  summarise(mean=mean(value, na.rm=T),
            sd=sd(value, na.rm=T),
            obs=sum(!is.na(value))) %>%
  ungroup()
kable(mit_descriptives, caption = "The descriptive statistics for data set using MIT export data")
```

And here the same information for the data using the Harvard export data:
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(knitr)
harv_descriptives <- read_csv("../data/dimension_endownment_data_HARV.csv") %>%
  tidyr::gather(variable, value, -location_code, -year) %>%
  group_by(variable) %>%
  summarise(mean=mean(value, na.rm=T),
            sd=sd(value, na.rm=T),
            obs=sum(!is.na(value))) %>%
  ungroup()
kable(harv_descriptives, caption = "The descriptive statistics for data set using Harvard export data")
```

# Further information

TBA
